An Efficient Audio Coding Scheme for Quantitative and Qualitative Large Scale Acoustic Monitoring Using the Sensor Grid Approach

### 2017-11-28 paper/articleV3.tex
v3pdf

\DeclareRobustCommand{\fg}[1]{{\sethlcolor{cyan}\hl{#1}}}

@@

% Authors, for the paper (add full first names)
\Author{\hl{F\'elix Gontier} $^{1}$, Mathieu Lagrange $^{1,}$\hl{*}, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}%Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.   and  ``*'' is newly added, please confirm. %R:confirmed that M.L. is the corresponding author

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad \hl{LS2N}\fg{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add it's zip code. %R: done
$^{2}$ \quad \hl{IFSTTAR, AME, LAE}\fg{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
$^{3}$ \quad \hl{ETIS, UMR 8051}%please add the complete location and add it's zip code. 
, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 \hl{Cergy-Pontoise}; %please add the city. %R: done
 catherine.lavandier@u-cergy.fr}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{The spreading of urban areas and the growth of human population worldwide \highlight{raise} societal and environmental concerns. To better address \highlight{these concerns}, the monitoring of the acoustic environment in urban \highlight{as well as} rural or wilderness areas is an important matter. \highlight{Building} on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue. In this kind of approach, the crucial question is the nature of the data that \highlight{are} transmitted from the sensors to the processing and archival servers. To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that \highlight{allows:} (1) the estimation of standard acoustic \highlight{indicators;} and (2) the recognition of acoustic events at state-of-the-art performance rate. The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source. The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, \highlight{are} not intelligible, thus protecting the privacy of citizens.}

@@

The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the \hl{SONYC} ({\url{htttp://wp.nyu.edu/sonyc}}) \cite{mydlarz2017implementation} and %Footnote are not allowed, pls conrfim. %R: ok
 \hl{CENSE} ({\url{htttp://cense.ifsttar.fr}}) \cite{picault2017} projects. To do so, considering the so-called ``sensor grid'' approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages. The sensor grid approach puts the focus \highlight{on:} (a) a distributed system of data acquisition with a large set of sensors; (b) the production and storage of a large dataset; and (c) its availability for intensive and open data analysis computation.

In such approach, the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, i.e., the approach shall be scalable. Second, the nodes shall be energy efficient, \highlight{and,  ideally,} autonomous, \highlight{to} ease the deployment of the sensor grid to the desired topology. Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to guarantee the privacy of the citizens. At the same time, the data stored shall remain as rich as \highlight{possible,} while maintaining a low bitrate for efficient transmission and storage.

In the case of urban acoustic monitoring, the data of interest typically \highlight{consist} of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.

In addition, considering sound sources allows \highlight{better assessing} the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017}. For instance, \highlight{bird song} and traffic noise with the same energy are perceived very differently. Most acoustic indicators used in current sound maps describe the global sound environment and lack information on its composition. The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments\highlight{ (see for example \cite{alsina2016design, app7020146, gloaguen2016estimating})}. Other indicators have been found to correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a well-designed source detection scheme in characterizing acoustic environments. This source detection step can\highlight{ be} operated online (on the sensors) or offline \highlight{(on the data servers),} leading to different grid designs (Figure \ref{fig:codingScheme}).

Performing the detection online (case B of Figure \ref{fig:codingScheme}) is efficient in terms of data storage as only the detected events are transmitted. This approach is thus currently considered in several applications in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. \highlight{However}, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels. Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.

Performing the detection offline has several benefits. First, the sensor task is much simpler and can thus be implemented on low energy consumption processors. This means that the sensors can be autonomous in terms of energy, which greatly eases the deployment of the network. Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline. Data can be re-analyzed following newer classification schemes or using new indicators. Though, transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy. Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}. Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition. \highlight{In addition, as the data are} transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.

@@

\highlight{To} promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research \hl{community} ({\url{https://github.com/felixgontier/cense-coder}}). The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding \highlight{scheme;} the experimental protocol designed to validate the proposed approach is described in \highlight{Section \ref{sec:protocol};} and results are discussed in Section \ref{sec:results}.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{figures/censeCoder}
\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic \highlight{environment:} in (\textbf{A}) the raw audio is transmitted; in (\textbf{B}) only the detected events; and in (\textbf{C}) a compressed spectral representation. Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
\label{fig:codingScheme}
\end{figure}

@@

The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental \highlight{data,} in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to ``bag-of-frames'' approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. \highlight{In addition}, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. Features can also be computed in other domains to better model signal properties. \mbox{For \highlight{instance,} \fg{Cai et al.} \cite{cai2006}} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features. Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}. Another promising solution is feature engineering via unsupervised learning, \highlight{which} \fg{Salamon et al.} \cite{salamon2015-2} implements with a clustering technique. More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments such as urban acoustic scenes \mbox{efficiently \citep{ntalampiras2012}. }A~more detailed review of used methods is available in \cite{chachada2013}.
%NOTE: Please add author names so that references are not subjects: "Smith et al. [ref] add..."

@@

A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}. \fg{Antoni} %newly added information, please confirm.
 \cite{antoni2010} \highlight{presents} an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering. The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards. It also meets the partition of unity principle over all frequency bins in the relevant range. Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} with 2nd order Butterworth time-domain filters, as shown in Figure~\ref{fig:freq_filt}. The major difference is that gains at cutoff frequencies are fixed at the optimal $-3$~dB value by design.
\vspace{-6pt}

@@

The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT). The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide ``fast'' or ``slow'' acoustic measurements. The data \highlight{are} zero-padded to the next power of two to improve computational efficiency. The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in Section \ref{sec:protocol}. The phase is discarded as it is not meaningful for third-octave analysis. Similarly, negative frequency components contain the same information as positive ones because the input signal is real. We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in~\cite{antoni2010} for $l = 2$ ({\highlight{when} implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p. 887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original \highlight{intention).}} We include analysis for bands $i$ from $-17$ to 13, i.e., center frequencies $f_i$ ranging from $20$~Hz to $20$~kHz with $f_0 = 1$~kHz. The representation is thus composed of 31 values.

@@

A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate while keeping the underlying information. At this point of the processing chain, the data \highlight{take} the form of a spectrogram with amplitude values represented on an arbitrary data type. It is therefore assimilable to a discrete distribution. By defining symbols as the possible values taken by the data, a discrete probability density function (PDF) can be expressed and estimated. The Shannon entropy then specifies the minimum average achievable output data rate for this given distribution, or average information content. The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign a code to each symbol so that the average output rate is the closest to the entropy. The resulting mapping function is called a Huffman dictionary.

The efficiency of the coding step thus directly depends on the entropy of the transmitted data. It~is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ \highlight{is} the numerical base in which the output code is represented. A lower entropy can be obtained with two factors. First, the dictionary \highlight{size,} i.e., the number of symbols must be kept low. This implies performing a quantization on the data resulting in a loss of precision. Second, the data distribution itself is important. Entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.

Considering an estimated PDF for our \highlight{data,} as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly \highlight{consist} of very low values and a direct quantization results in most of the information being lost. We therefore flatten the PDF by taking the logarithm of the representation (top-right). This allows to better use the available range of symbols. A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf} (bottom-left). Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies between consecutive frames. This effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf} bottom-right), yielding a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy. In~the example shown here, the entropy before $\Delta$-compression is $H_{log} = 6.24~sh$ which is reduced to $H_{\Delta} = 3.54~sh$.
\vspace{-6pt}

\begin{figure}[H]
	\centering
		\includegraphics[width=0.78\textwidth]{figures/pdf.eps}
	\caption{Example of estimated probability density functions of the data throughout the encoding step. Unchanged output of the representation step (\textbf{top}-\textbf{left}), concentrated towards very low values. PDF ``flattening'' effect induced by logarithm application (\textbf{top}-\textbf{right}). \highlight{Here,} values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (\textbf{bottom}-\textbf{left}). Output of the $\Delta$ compression  (\textbf{bottom}-\textbf{right}), with desirable probabilities as the input to a Huffman algorithm.}
	\label{fig:pdf}
\end{figure}

@@

\highlight{To} assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}. This toolbox's implementation shows less than $0.1$~dB error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements. We study both ``fast'' computation with 125~ms windows and ``slow'' 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this \highlight{reason,} we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

\highlight{To} ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset~\cite{salamon2014}. It features about 9 h of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 s each. The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren,\highlight{ and} street music), and distributed in 10 independent folds. A method and baseline results are also provided for the classification task. In this study, audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.

The aim of this experiment is two-fold: to evaluate the global loss of information induced by the coding process, and to evaluate the adequacy of third-octave bands indicators for classification. As~studying the best performing classical \hl{models} \citep{ntalampiras2013}, %Reference [49] is cited after [47] directly, which is out of order. Please confirm.
deep learning approaches \citep{salamon2017} or unsupervised feature learning is beyond the scope of this paper, we choose to replicate the baseline models and results proposed in \cite{salamon2014}.

@@

\begin{figure}[H]
	\centering
		\includegraphics[width=0.8\textwidth]{figures/class.pdf}
	\caption{Classification process flowchart. Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model. Cross-validation is achieved by independantly training and testing the models with each of the 10 combinations of a 90--\hl{10}\% training\highlight{--}validation dataset separation.}% changed from ``10'' to ``100'', please confirm.
%NOTE: 90%/10%?
%R: 90% of the dataset used for training, the remaining 10% for validation
	\label{fig:class_flwc}
\end{figure}

@@

It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data \highlight{are} transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible. Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.

The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} field. The readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}. \highlight{However}, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances. \highlight{Thus}, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.

\highlight{To} decrease the intelligibility, several approaches can be considered. First, a speech versus non speech detector can be implemented on the sensor. If some speech is detected, the data \highlight{are} not transmitted. This approach is however prone to failure of the detector and will lead to unavailability of data during speech time \highlight{periods,} which might compromise the relevance of some indicators.

@@

The same set of parameters as in bitrate evaluation is used to study the impact of their tuning on sound event recognition performance. This experiment aims at finding ways to further reduce the encoded data size without strongly affecting detection performance. Results of the four presented classification methods (\hl{Section} \ref{sec:event_p}) are provided for the sake of completeness.% newly added information, please confirm. R:correct

>>>>

@@

% Authors, for the paper (add full first names)
\Author{{F\'elix Gontier} $^{1}$, Mathieu Lagrange $^{1,}${*}, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}%Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.   and  ``*'' is newly added, please confirm. %R:confirmed that M.L. is the corresponding author

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad {LS2N}{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
$^{2}$ \quad {IFSTTAR, AME, LAE}{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
$^{3}$ \quad {ETIS, UMR 8051}%please add the complete location and add it's zip code.
, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 {Cergy-Pontoise}; %please add the city. %R: done
 catherine.lavandier@u-cergy.fr}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{The spreading of urban areas and the growth of human population worldwide {raise} societal and environmental concerns. To better address {these concerns}, the monitoring of the acoustic environment in urban {as well as} rural or wilderness areas is an important matter. {Building} on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue. In this kind of approach, the crucial question is the nature of the data that {are} transmitted from the sensors to the processing and archival servers. To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that {allows:} (1) the estimation of standard acoustic {indicators;} and (2) the recognition of acoustic events at state-of-the-art performance rate. The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source. The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, {are} not intelligible, thus protecting the privacy of citizens.}

@@

The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the {SONYC} ({\url{htttp://wp.nyu.edu/sonyc}}) \cite{mydlarz2017implementation} and %Footnote are not allowed, pls conrfim. %R: ok
 {CENSE} ({\url{htttp://cense.ifsttar.fr}}) \cite{picault2017} projects. To do so, considering the so-called ``sensor grid'' approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages. The sensor grid approach puts the focus {on:} (a) a distributed system of data acquisition with a large set of sensors; (b) the production and storage of a large dataset; and (c) its availability for intensive and open data analysis computation.

In such approach, the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, i.e., the approach shall be scalable. Second, the nodes shall be energy efficient, {and,  ideally,} autonomous, {to} ease the deployment of the sensor grid to the desired topology. Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to guarantee the privacy of the citizens. At the same time, the data stored shall remain as rich as {possible,} while maintaining a low bitrate for efficient transmission and storage.

In the case of urban acoustic monitoring, the data of interest typically {consist} of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.

In addition, considering sound sources allows {better assessing} the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017}. For instance, {bird song} and traffic noise with the same energy are perceived very differently. Most acoustic indicators used in current sound maps describe the global sound environment and lack information on its composition. The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments{ (see for example \cite{alsina2016design, app7020146, gloaguen2016estimating})}. Other indicators have been found to correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a well-designed source detection scheme in characterizing acoustic environments. This source detection step can{ be} operated online (on the sensors) or offline {(on the data servers),} leading to different grid designs (Figure \ref{fig:codingScheme}).

Performing the detection online (case B of Figure \ref{fig:codingScheme}) is efficient in terms of data storage as only the detected events are transmitted. This approach is thus currently considered in several applications in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. {However}, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels. Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.

Performing the detection offline has several benefits. First, the sensor task is much simpler and can thus be implemented on low energy consumption processors. This means that the sensors can be autonomous in terms of energy, which greatly eases the deployment of the network. Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline. Data can be re-analyzed following newer classification schemes or using new indicators. Though, transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy. Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}. Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition. {In addition, as the data are} transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.

@@

{To} promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research {community} ({\url{https://github.com/felixgontier/cense-coder}}). The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding {scheme;} the experimental protocol designed to validate the proposed approach is described in {Section \ref{sec:protocol};} and results are discussed in Section \ref{sec:results}.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{figures/censeCoder}
\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic {environment:} in (\textbf{A}) the raw audio is transmitted; in (\textbf{B}) only the detected events; and in (\textbf{C}) a compressed spectral representation. Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
\label{fig:codingScheme}
\end{figure}

@@

The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental {data,} in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to ``bag-of-frames'' approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. {In addition}, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. Features can also be computed in other domains to better model signal properties. \mbox{For {instance,} {Cai et al.} \cite{cai2006}} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features. Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}. Another promising solution is feature engineering via unsupervised learning, {which} {Salamon et al.} \cite{salamon2015-2} implements with a clustering technique. More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments such as urban acoustic scenes \mbox{efficiently \citep{ntalampiras2012}. }A~more detailed review of used methods is available in \cite{chachada2013}.
%NOTE: Please add author names so that references are not subjects: "Smith et al. [ref] add..."

@@

A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}. {Antoni} %newly added information, please confirm.
 \cite{antoni2010} {presents} an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering. The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards. It also meets the partition of unity principle over all frequency bins in the relevant range. Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} with 2nd order Butterworth time-domain filters, as shown in Figure~\ref{fig:freq_filt}. The major difference is that gains at cutoff frequencies are fixed at the optimal $-3$~dB value by design.
\vspace{-6pt}

@@

The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT). The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide ``fast'' or ``slow'' acoustic measurements. The data {are} zero-padded to the next power of two to improve computational efficiency. The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in Section \ref{sec:protocol}. The phase is discarded as it is not meaningful for third-octave analysis. Similarly, negative frequency components contain the same information as positive ones because the input signal is real. We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in~\cite{antoni2010} for $l = 2$ ({{when} implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p. 887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original {intention).}} We include analysis for bands $i$ from $-17$ to 13, i.e., center frequencies $f_i$ ranging from $20$~Hz to $20$~kHz with $f_0 = 1$~kHz. The representation is thus composed of 31 values.

@@

A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate while keeping the underlying information. At this point of the processing chain, the data {take} the form of a spectrogram with amplitude values represented on an arbitrary data type. It is therefore assimilable to a discrete distribution. By defining symbols as the possible values taken by the data, a discrete probability density function (PDF) can be expressed and estimated. The Shannon entropy then specifies the minimum average achievable output data rate for this given distribution, or average information content. The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign a code to each symbol so that the average output rate is the closest to the entropy. The resulting mapping function is called a Huffman dictionary.

The efficiency of the coding step thus directly depends on the entropy of the transmitted data. It~is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ {is} the numerical base in which the output code is represented. A lower entropy can be obtained with two factors. First, the dictionary {size,} i.e., the number of symbols must be kept low. This implies performing a quantization on the data resulting in a loss of precision. Second, the data distribution itself is important. Entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.

Considering an estimated PDF for our {data,} as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly {consist} of very low values and a direct quantization results in most of the information being lost. We therefore flatten the PDF by taking the logarithm of the representation (top-right). This allows to better use the available range of symbols. A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf} (bottom-left). Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies between consecutive frames. This effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf} bottom-right), yielding a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy. In~the example shown here, the entropy before $\Delta$-compression is $H_{log} = 6.24~sh$ which is reduced to $H_{\Delta} = 3.54~sh$.
\vspace{-6pt}

\begin{figure}[H]
	\centering
		\includegraphics[width=0.78\textwidth]{figures/pdf.eps}
	\caption{Example of estimated probability density functions of the data throughout the encoding step. Unchanged output of the representation step (\textbf{top}-\textbf{left}), concentrated towards very low values. PDF ``flattening'' effect induced by logarithm application (\textbf{top}-\textbf{right}). {Here,} values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (\textbf{bottom}-\textbf{left}). Output of the $\Delta$ compression  (\textbf{bottom}-\textbf{right}), with desirable probabilities as the input to a Huffman algorithm.}
	\label{fig:pdf}
\end{figure}

@@

{To} assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}. This toolbox's implementation shows less than $0.1$~dB error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements. We study both ``fast'' computation with 125~ms windows and ``slow'' 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this {reason,} we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

{To} ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset~\cite{salamon2014}. It features about 9 h of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 s each. The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren,{ and} street music), and distributed in 10 independent folds. A method and baseline results are also provided for the classification task. In this study, audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.

The aim of this experiment is two-fold: to evaluate the global loss of information induced by the coding process, and to evaluate the adequacy of third-octave bands indicators for classification. As~studying the best performing classical {models} \citep{ntalampiras2013}, %Reference [49] is cited after [47] directly, which is out of order. Please confirm.
deep learning approaches \citep{salamon2017} or unsupervised feature learning is beyond the scope of this paper, we choose to replicate the baseline models and results proposed in \cite{salamon2014}.

@@

\begin{figure}[H]
	\centering
		\includegraphics[width=0.8\textwidth]{figures/class.pdf}
	\caption{Classification process flowchart. Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model. Cross-validation is achieved by independantly training and testing the models with each of the 10 combinations of a 90--{10}\% training{--}validation dataset separation.}% changed from ``10'' to ``100'', please confirm.
%NOTE: 90%/10%?
%R: 90% of the dataset used for training, the remaining 10% for validation
	\label{fig:class_flwc}
\end{figure}

@@

It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data {are} transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible. Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.

The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} field. The readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}. {However}, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances. {Thus}, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.

{To} decrease the intelligibility, several approaches can be considered. First, a speech versus non speech detector can be implemented on the sensor. If some speech is detected, the data {are} not transmitted. This approach is however prone to failure of the detector and will lead to unavailability of data during speech time {periods,} which might compromise the relevance of some indicators.

@@

The same set of parameters as in bitrate evaluation is used to study the impact of their tuning on sound event recognition performance. This experiment aims at finding ways to further reduce the encoded data size without strongly affecting detection performance. Results of the four presented classification methods ({Section} \ref{sec:event_p}) are provided for the sake of completeness.% newly added information, please confirm. R:correct
